An approach for cloud correction of operational humidity channels

### 2020-09-10 Article/ici_submm_cloudcorr.tex
Started on the Introduction in the article. Cleaning of references.

@@

\title{TEXT}

% \Author[affil]{given_name}{surname}

\Author[]{}{}
\Author[]{}{}
\Author[]{}{}

\affil[]{ADDRESS}
\affil[]{ADDRESS}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

%% If an author is deceased, please mark the respective author name(s) with a dagger, e.g. "\Author[2,$\dag$]{Anton}{Aman}", and add a further "\affil[$\dag$]{deceased, 1 July 2019}".

@@

\correspondence{NAME (EMAIL)}

\runningtitle{TEXT}

\runningauthor{TEXT}

@@

\introduction  %% \introduction[modified heading if necessary]

@@

The absorption model takes into account the effect from nitrogen \citep{pwr:93}, oxygen \citep{pwr:93} and water vapour \citep{ellison2007permittivity}. LWC is taken from ERA-Interim and is assumed to be totally absorbing. In the
mapping of CloudSat reflectivities to RWC and IWC a total separation between
liquid and ice phase is assumed. All scattering hydrometeors at temperatures
above 0$^\circ$C are assumed to be rain, and all below 0$^\circ$C are assumed
to be ice hydrometeors. For RWC the particle size distribution of \citet{abel2012improved} is applied. The PSD of IWC follows the basic formulation applied in DARDAR (\verb http://www.icare.univ-lille1.fr/projects/dardar), using latest parameter values (i.e.\ $\alpha$ and $\beta$) as given by
\citet{amt-12-2819-2019}. This PSD can be considered as a ``two moment''
scheme, but is here applied in a one moment manner by setting $N_0^*$ (as a
function of temperature) following Table~5 of \citet{delanoe2014normalized},
and letting the radar reflectivity set the remaining moment.
Single scattering data are taken from \citet{eriksson:agene:18}. For ice
hydrometeors, three habits are applied: Perpendicular 3-bullet rosette, Large
plate aggregate and Large column aggregate. In the last two cases, the
aggregates are complemented with single crystal data to also cover smaller
sizes. These data describe particles assumed to have a totally random
orientation. To apply oriented particles is much more computationally costly
and could not be accommodated inside the study. The land emissivity was taken from TELSEM \citep{aires2011tool} and the Ocean/water from TESSEM \citep{prigent2017sea}. For each atmopsheric case, both ''clear-sky'' and ``all-sky'' calculations were performed. In the former, all impact of all hydrometeors were set to zero, while in the latter, IWC and RWC derived from CloudSat reflectivities and LWC from ERA-Interim were taken into account. Both sets of calculations were made by ARTS's interface to the RT4 solver \citep{evans1995microwavec}. To avoid a possible bias between clear-sky and all-sky for insignificant hydrometeor contents, the same ``scattering solver'' was used for both calculations. The first two elements of the
Stokes vector were calculated.

@@

These results show that both QRNN-simple and QRNN-all are successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high cloud impact. This is not unexpected, as such cases form a small subset of the training set and their priori distribution could be different from the the entire dataset. 
Since such cases form only a fraction of the training dataset, it can be hard to train the model to predict them accurately. A larger training dataset is needed to increase the representation of such cases in QRNN.    
\subsection{Discussion}

@@

\subsection{Data}
\subsubsection{Artic Weather Satellite}
The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA Earth Watch 
Programme Element. It is a small platform carrying a single across-track scanning microwave radiometer. The main objective of AWS will be to improve representation of Artic and sub-Arctic weather in NWP models and improve the global weather forecasts. AWS will will have channels receiving frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a detailed description of the AWS channels see \citep{eriksson-etal_AWS_2020}, while a brief summary of AWS channels relevant to this study are provided in Table~\ref{tab:specifications_AWS}
\begin{table*}[t]
	\label{tab:ICI_MWI_channels}	
	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
	\begin{tabular}{lrr}
		\tophline
		Channel & Frequency 	& Bandwidth  \\
				& [GHz]			& [MHz]		\\
		\middlehline
		AWS-32	&	176.311    & 2000 		\\
		AWS-33	&	178.811    & 2000 		\\
		AWS-34	&	180.311    & 1000 		\\
		AWS-35	&	181.511    & 1000 		 \\
		AWS-36	&	182.311    & \phantom{0}500 	 \\
	    AWS-41    & 325.15$\pm$6.60    & 2800 \\
		AWS-42    & 325.15$\pm$4.10    & 1800  \\
		AWS-43    & 325.15$\pm$2.40    & 1200 \\
		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
			\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}

>>>>

\newcommand{\todo}[1]{{\color{red} #1}}

@@

\title{An approach for cloud correction of operational humidity channels}

\Author[1]{Inderpreet}{Kaur}
\Author[1]{Patrick}{Eriksson}
\Author[1]{Simon}{Pfreundschuh}

\affil[1]{Department of Space, Earth and Environment, Chalmers University of
  Technology, Gothenburg, Sweden}

@@

\correspondence{Inderpreet Kaur <kauri@chalmers.se>}

\runningtitle{A cloud correction approach}

\runningauthor{Kaur et al.}

@@

\introduction
%
\todo{Add references and do a literature search on cloud filtering}

Satellite observations of humidity inside the troposphere are mainly performed
by downward-looking sensors. Among this class of observations, the frequency
range around 183\,GHz has a special role. Water vapour has a noticeable
transition at 22\,GHz, but it is relatively weak and only column values can be
derived \citep[e.g.][]{schluessel1990atmospheric} for the observation geometry
of concern. The first transition in the microwave region that can be used to
derive altitude information, i.e.\ can be used for ``sounding'', is the one at
183.31\,GHz \citep[e.g.][]{kakar1983retrieval}. On the other hand, at
infrared wavelengths a high number of water vapour transitions are found,
including some of high strength. As a consequence, infrared sounders can
provide humidity profiles with high precision and good vertical resolution, but
with strong limitions imposed by clouds. To be able to also sense humidity
inside and below clouds weather satellites are since some time equipped with
channels around 183\,GHz. Today such channels are part several sensors, such as
MHS (Microwave Humidity Sounder) and ATMS (Advanced Technology Microwave
Sounder ).

Precipiation and most dense clouds, particularly if found at high altitude, can
still afffect measured radiances around 183\,GHz. As the impact from the
hydrometeors is then dominated by scattering, the complexity of the analysis of
the data increases dramatically and there exists a need to identify such cases.
This is normally denoted as cloud filtering, to obtain data of ``clear sky''
character. Such filtering has been applied to derive climate records, and is
also essentail in studies of the agreement between observations and
simulations. Examples on cloud filtering methods used for these applicatons are
\todo{(refs)}. These methods arebased on the 183\,GHz data alone and rules on
the brightness temperatures of different channels, including the difference
between channels, are applied to remove cloud affected data.

The main motivation for introducing 183\,GHz channels in operational sensors is
numerical weather prediction (NWP). Usage of microwave data in NWP by
``all-sky'' assimilation is growing, but 183\,GHz data are still mainly used in
a clear sky fashion. The later is particularly true in NWP of regional scope,
all-sky assimilation of 183\,GHz at many national weather agencies will likely
not be reached in many years. The cloud filtering in NWP differs between
centres, but normally \dots

All above filtering ...

@@

The absorption model takes into account the effect from nitrogen
\citep{pwr:93}, oxygen \citep{pwr:93} and water vapour
\citep{ellison2007permittivity}. LWC is taken from ERA-Interim and is assumed
to be totally absorbing. In the mapping of CloudSat reflectivities to RWC and
IWC a total separation between liquid and ice phase is assumed. All scattering
hydrometeors at temperatures above 0$^\circ$C are assumed to be rain, and all
below 0$^\circ$C are assumed to be ice hydrometeors. For RWC the particle size
distribution of \citet{abel2012improved} is applied. The PSD of IWC follows the
basic formulation applied in DARDAR (\verb
 http://www.icare.univ-lille1.fr/projects/dardar), using latest parameter
 values (i.e.\ $\alpha$ and $\beta$) as given by \citet{cazenave2019evolution}.
 This PSD can be considered as a ``two moment'' scheme, but is here applied in
 a one moment manner by setting $N_0^*$ (as a function of temperature)
 following Table~5 of \citet{delanoe2014normalized}, and letting the radar
 reflectivity set the remaining moment. Single scattering data are taken from
 \citet{eriksson:agene:18}. For ice hydrometeors, three habits are applied:
 Perpendicular 3-bullet rosette, Large plate aggregate and Large column
 aggregate. In the last two cases, the aggregates are complemented with single
 crystal data to also cover smaller sizes. These data describe particles
 assumed to have a totally random orientation. To apply oriented particles is
 much more computationally costly and could not be accommodated inside the
 study. The land emissivity was taken from TELSEM \citep{aires2011tool} and the
 Ocean/water from TESSEM \citep{prigent2017sea}. For each atmopsheric case,
 both ''clear-sky'' and ``all-sky'' calculations were performed. In the former,
 all impact of all hydrometeors were set to zero, while in the latter, IWC and
 RWC derived from CloudSat reflectivities and LWC from ERA-Interim were taken
 into account. Both sets of calculations were made by ARTS's interface to the
 RT4 solver \citep{evans1995microwavec}. To avoid a possible bias between
 clear-sky and all-sky for insignificant hydrometeor contents, the same
 ``scattering solver'' was used for both calculations. The first two elements
 of the Stokes vector were calculated.

@@

These results show that both QRNN-simple and QRNN-all are successful in
providing well calibrated probabilistic predictions of the posterior
distributions except for few cases associated with high cloud impact. This is
not unexpected, as such cases form a small subset of the training set and their
priori distribution could be different from the the entire dataset. Since such
cases form only a fraction of the training dataset, it can be hard to train the
model to predict them accurately. A larger training dataset is needed to
increase the representation of such cases in QRNN.

\subsection{Discussion}

@@

\subsection{Data}
\subsubsection{Artic Weather Satellite}
The Arctic Weather Satellite (AWS) is a small satellite mission approved as ESA
Earth Watch Programme Element. It is a small platform carrying a single
across-track scanning microwave radiometer. The main objective of AWS will be
to improve representation of Artic and sub-Arctic weather in NWP models and
improve the global weather forecasts. AWS will will have channels receiving
frequencies around 89\,GHz, 165.5\,GHz, 183\,GHz, 229\,GHz and 325\,GHz. For a
detailed description of the AWS channels see \citep{eriksson2020study}, while a
brief summary of AWS channels relevant to this study are provided in
Table~\ref{tab:specifications_AWS}.

% Let's try avoid citing the AWS report. If we do, we must put it on
% research.chalmers.se

\begin{table*}[t]
	\label{tab:ICI_MWI_channels}	
	\caption{Specifications of AWS channels around 183\,GHz and 325\,GHz.}
	\begin{tabular}{lrr}
		\tophline
		Channel & Frequency 	& Bandwidth  \\
				& [GHz]			& [MHz]		\\
		\middlehline
		AWS-32	&	176.311    & 2000 		\\
		AWS-33	&	178.811    & 2000 		\\
		AWS-34	&	180.311    & 1000 		\\
		AWS-35	&	181.511    & 1000 		 \\
		AWS-36	&	182.311    & \phantom{0}500 	 \\
	    AWS-41    & 325.15$\pm$6.60    & 2800 \\
		AWS-42    & 325.15$\pm$4.10    & 1800  \\
		AWS-43    & 325.15$\pm$2.40    & 1200 \\
		AWS-44    & 325.15$\pm$1.20    & \phantom{0}800  \\
			\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
